---
title: "List, Factor, Dataframe"
author: "Jesse"
date: "2019¦~11¤ë4¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```
**List, Factor, DataFrame** are three important data structures that we would use a lot during data storage.  
After getting furthur knowledge about them, we can decide what type of data strucutres we use to store data.



# List
List is a data structure having components of mixed data types.  

## Create a list.
We use `list()` to create a list.

```{r}
x <- list(2.5, TRUE, 2)
```

As you can see, a list *x* with components consisting of  *numeric*, *logical* and *integer* .  

We can use `str()` function to examine its structure.

```{r}
str(x)
```


Also, we can assign *called tags* so that it would be easier to reference the components of the list.  
It's optional.


```{r}
x <- list("a" = 2.5, "b" = TRUE, "c" = 2)
str(x)
```

## Data Extraction

```{r}
x <- list("name" = "John", "age" = 19, "language" = c("Chinese", "English"))
```

Index using integer vector

```{r}
x[c(1:2)]
```

Using negative inteer to exclude certain index.

```{r}
x[-3]
```

Index using character vector

```{r}
x[c(T,F,F)]
```

Index using called tags
```{r}
x[c("age", "language")]
```

Nevertheless, indexing with `[` will return sublist not the content inside the component.  
We can use `[[` to get the content.

```{r}
x["age"]
typeof(x["age"])

x[["age"]]
typeof(x[["age"]])
```

When trying to get the element of certain sublist,  
we still need to use `[[`

```{r}
x[['language']][1]
```


## Modification
Choose certain component and use assignment operator could modify the list.

```{r}
x[["name"]] <- "James"
x
```

## Add components
We can assign values with new tags.

```{r}
x[["married"]] <- FALSE
x
```

or by index.

```{r}
x[[5]] <- 6
x
```

## Delete components
By assigning `NULL` to it, we can delete the component.

```{r}
x[["married"]] <- NULL
str(x)
```

```{r}
x[[4]] <- NULL
x
```

### Question
Below is some information about John, Mary, and Jean.

John, Teacher, 21-year-old, not married.  
Mary Professor, 25-year-old, married.  
Jean Nurse, 30-year-old, not married.  

1. Try to convert each person's information into a list.(3 lists in total)  
2. Try to make a list of all informatioin.  


# Factor
Factor is a data structure used for taking only predefined, finite number of values.  
For example, marital status can only contain with `single, married, separated, divoced, widowed` in it.  
For thesse possible, predifined, distinct values, we called it *levels*.


## Create
We can create a factor using the function `factor()`.

```{r}
x <- factor(c("single","married", "married"))
x
```
```{r}
x <- factor(c("single","married", "married"), levels = c("single", "married", "divorced"))
x
```

## Extraction
Extracting elements of a factor is very much similar to that of vectors.

```{r}
x
x[2]
x[c(1:2)]
x[-2] # exclude the second element
x[c(T,F,T)] #using logical vector
```

## Modification
We can modify elemts using assignments.  
**Nevertheless, we cannot assign values not include in predifined values.**


```{r}
x
x[2] <- "divorced"
x[3] <- "separated"
```

If you think it necessary, you should add it to the level first.


```{r}
levels(x) <- c(levels(x), "separated")
x[3] <- "separated"
x
```


# DataFrame
Dataframe is a *two* dimensional data structure.  
It is a sppecial case of lists.  
When we use data input functions like `read.csv()`,  
it read data into a data frame.

## Create
We can create a dataframe using the `data.frame` function.

```{r}
x <- data.frame("No" = 1:3, "Age" = 21:19, "Married" = c(T,F,F), "Names" = c("Doris", "Daniel", "Lucy"))
str(x)
```

** By default, dataframe would converts character vector into factor.**
We cann pass the argument `stringAsFactors=FALSE` to stop this.

```{r}
x <- data.frame("No" = 1:3, "Age" = 21:19, "Married" = c(T,F,F), "Names" = c("Doris", "Daniel", "Lucy"), stringsAsFactors = FALSE)
str(x)
```

If you wanna assign row_names, we can use `rownames()` function.  
```{r}
rownames(x) <- c("One", "Two", "Three")
```


## Data Extraction
We can use `[`, `[[` and `$` operator to access columns of data frame.

```{r}
x["Names"]
x$Names
x[["Name"]]
x[[3]]
```

### Question: What's the difference between the previous four way?

Also, we can extract data by providing index for row and column.

```{r}
x[1,1]
x[2,]
x["One",]
x["One","Names"]
```


## Modification
Dataframes can be modified like we modified matrices.

```{r}
x[1,1] <- 6 
x
x["Daniel", "Age"] <- 60
x
```

## Add components
We can add rows to a data frame using the `rbind()` function.

```{r}
rbind(x, Jesse = list(6,22,FALSE, "Jesse"))
rbind(x, list(5,20,TRUE,"Flora"))
```

Also, we could use `cbind()` to add columns.

```{r}
cbind(x, Children=c(1:4))

```

The most commonly used one is to use `$` to add new columns.

```{r}
x$Language <- c("Chinese","Chinese","Chinese","English")
```


## Delete components
By assigning `NULL` to it, we can delete the component.

```{r}
x$No <- NULL
x
```


### Question

1. Please convert information about James, Jason, Johnny into dataframe.

- Name, Age, Language, Relationship  
- James, 20, speaks Chinese, single  
- Jason, 22, speaks English, not single  
- Johnny, 30, speaks spanish, not single  

2. Extract Jason's data / Extract Language data / Extract James' Age

3. We found that Jason is actually 30 years old. Try correcting it.

4. Add Ted's data into the dataframe.

- Ted, 30, speaks English, single

5. To keep privacy of our data, try drop the Name Column.