---
title: "Advanced Data Visualization"
author: "Jesse"
date: "2019¦~9¤ë23¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
library(tidyverse)
gpa = read.csv("C:/Users/asus/Desktop/TA/TA session/week2/gpa.csv")
```

## Basic Plots
We just try doing scatterplots and histogram during last class.
Today we gonna have more plots to support our visulization.

For futhur learning on ggplot2, the following link is the official instruction for ggplot package,  
where you can learn different plots and do some customized settings.  
https://ggplot2.tidyverse.org/reference/index.html

### Scatterplot
```{r}
ggplot(data=gpa) +
  geom_point(mapping = aes(x=out, y=gpa))
```

### Smoothed mean line
```{r}
ggplot(data=gpa) +
  geom_smooth(mapping = aes(x=out, y=gpa))
```

### Barplot¡BHistogram
```{r}
ggplot(data = gpa) +
  geom_bar(mapping = aes(x=gender))

ggplot(data = gpa) +
  geom_histogram(mapping = aes(x=gpa))
```

**Bar plots provide a visual presentation of categorical data.**
**Histograms are used to plot denstiy of interval data.**

### Boxplot
````{r}
ggplot(data = gpa) + 
  geom_boxplot(mapping = aes(x=0.5, y=out))
ggplot(data = gpa) + 
  geom_boxplot(mapping = aes(group=gender, x=gender, y=out))
```

### Dotplot
```{r}
ggplot(data = gpa) + 
  geom_dotplot(mapping = aes(x=out))
ggplot(data = gpa) + 
  geom_dotplot(mapping = aes(x=0.5, y=out), binaxis = "y")
```


After learning basic plots,  
Now we can try do some advanced settings toward our plots.  

## Advanced Settings

### Title
```{r}
ggplot(data=gpa) +
  geom_point(mapping = aes(x=out, y=gpa)) +
  scale_x_continuous("Number of Nights going out") + 
  scale_y_continuous("GPA") + 
  ggtitle("Out ~ GPA")
```

### Breaks
```{r}
ggplot(data=gpa) +
  geom_point(mapping = aes(x=out, y=gpa)) +
  scale_x_continuous("Number of Nights going out", breaks = c(0,0.5,1,1.5,2,2.5,3,3.5,4)) + 
  scale_y_continuous("GPA", breaks = c(3.2,3.4,3.6,3.8,4,4.2,4.4)) + 
  ggtitle("Out ~ GPA")
```

### Labels
```{r}
ggplot(data=gpa) +
  geom_point(mapping = aes(x=out, y=gpa)) +
  scale_x_continuous("Number of Hours going out", breaks = c(0,0.5,1,1.5,2,2.5,3,3.5,4), labels = c(0,3,6,9,12,15,18,21,24)) + 
  scale_y_continuous("GPA", breaks = c(3.2,3.4,3.6,3.8,4,4.2,4.4)) + 
  ggtitle("Out Hours ~ GPA")
```

### Advanced Histogram
**bins**¡B**col**
```{r}
ggplot(data = gpa) + 
  geom_histogram(mapping = aes(x=gpa), bins = 10)
ggplot(data = gpa) + 
  geom_histogram(mapping = aes(x=gpa), bins = 10, col="black")
```

### Advanced Barplot
**position**
```{r}
ggplot(data = gpa) + 
  geom_bar(mapping = aes(x=out, fill=gender))
ggplot(data = gpa) + 
  geom_bar(mapping = aes(x=out, fill=gender), position = "dodge")
ggplot(data = gpa) + 
  geom_bar(mapping = aes(x=out, fill=gender), position = "fill") + 
  scale_y_continuous("Frequency", breaks = c(0,0.25,0.5,0.75,1), labels = c("0","25%","50%","75%","100%"))
```

### Advanced Dotplot
**stackdir**
```{r}
ggplot(data = gpa) + 
  geom_dotplot(mapping = aes(x=out), stackdir = "center")
```

### Overlay
```{r}
ggplot(data=gpa) +
  geom_point(mapping = aes(x=out, y=gpa)) +
  geom_smooth(mapping = aes(x=out, y=gpa))
```