---
title: "Descriptive Summary Statistics Tables"
author: "Jesse"
date: "2019¦~9¤ë23¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
gpa = read.csv("C:/Users/asus/Desktop/TA/TA session/week2/gpa.csv")
```

# %>% pipe
f(x);  
g(x);  
h(x);  
**Too much effort**  
With %>%,  
we can make it more clear: x %>% f() %>% g() %>% h();  

```{r}
x <- 6
x <- exp(x)
x <- log(x)

x %>% exp() %>% log()
```

# Summarize()
Reference: https://www.rdocumentation.org/packages/dplyr/versions/0.7.8/topics/summarise  
With summarize(), we can get descriptive statistics such as mean, median... of our data.  
```{r}
gpa %>%
  summarize(mean(gpa),
            median(gpa))

```
Meanwhile, as in summarize() function, we create new variables, therefore we can give names toward our statistics data.  
Moreover, store the table with variable.  
```{r}
gpa %>%
  summarize(mean = mean(gpa),
            median = median(gpa))
gpa %>%
  summarise(q25 = quantile(gpa, .25),
            q75 = quantile(gpa, .75))
```
```{r}
gpa_summary_statistics <- gpa %>%
  summarise(mean = mean(gpa),
            median = median(gpa),
            q25 = quantile(gpa, .25),
            q75 = quantile(gpa, .75)
            )
gpa_summary_statistics
```

# Contingency Table
Reference: https://www.datacamp.com/community/tutorials/contingency-tables-r  
With table() function, we can create contingency table.
```{r}
table(gpa$gender)
```

Fraction of marginal table would work with function `prop.table()`.
```{r}
prop.table(table(gpa$gender))
```

Of course, we can store it it variable.
```{r}
gpa_gender_proportion <- prop.table(table(gpa$gender))
gpa_gender_proportion
```

Moreover, we can create two-way contingency tables.
```{r}
table(gpa$sleepnight, gpa$gender)
prop.table(table(gpa$sleepnight, gpa$gender))
```

To make the table more clear, we can give names to each dimensions with `dnn`  
```{r}
prop.table(table(gpa$sleepnight, gpa$gender,dnn=c("SleepNight", "Gender")),margin = 1)
```

And store it in variable.
```{r}
sleepnight_gender <- table(gpa$sleepnight, gpa$gender)
sleepnight_gender
```

Last but not least, we can add **total** by `addmargins`  
```{r}
addmargins(sleepnight_gender)
```

