---
title: "Distribution"
author: "Jesse Chang"
date: "2019¦~10¤ë7¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```

# Uniform Distribution  

**dunif(x, min=0, max=1)**: density.  
x = vector of quantiles.  

**runif(n, min=0, max=1)**  

## Density curve.
```{r}
x <- seq(0,1,by=0.02)
y <- dunif(x, 0, 1)
ggplot() + 
  geom_line(mapping = aes(x=x, y=y))
```
## Sampling

```{r}
x <- runif(52,0,1)
hist(x)
```

`hist()` is a easier way to conduct histogram.   
You may still use `ggplot() + geom_histogram` to reach the similar result.  



# Normal Distribution  

**dnorm(x, min=0, max=1)**: density.  
x = vector of quantiles.  

**rnorm(n, min=0, max=1)**  

## Density curve.
```{r}
x <- seq(-2,2,by=0.02)
y <- dnorm(x, 0, 1)
ggplot() + 
  geom_line(mapping = aes(x=x, y=y))
```
## Sampling

```{r}
x <- rnorm(200,0,1)
hist(x)
```


# Binomial Distribution  

**dbinom(x, size, prob)**: density  
**rbinom(n, size, prob)**  

## Density curve.
```{r}
x <- seq(0,100)
y <- dbinom(x, 100, 0.5)
ggplot() + 
  geom_line(mapping = aes(x=x, y=y))
```


## Sampling

```{r}
x <- rbinom(50,100,0.5)
hist(x)
```

```{r}
x <- rbinom(200,100,0.5)
hist(x)
```

