---
title: "Random¡BLoop"
author: "Jesse Chang"
date: "2019¦~10¤ë8¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```

# Random Numbers

## Uniform distribution  
**runif(n, min = 0, max = 1)**  
`runif()` function enables us to generate random numbers based on *uniform distribution*.  
Minimum number would be set as 0 on default,  
and Maximum number would be set as 1 on default.  

```{r}
runif(1)
```

```{r}
runif(4)
```

```{r}
runif(3,2,5)
```

```{r}
runif(5,min = 0, max = 50)
```


## Normal Distribution
**rnorm(n, mean=0, sd=1)**  
`rnorm()` function enables us to generate random numbers based on *normal distribution*.  
Mean would be set as 0 on default,  
and Standard Deviation would be set as 1 on default.  



```{r}
rnorm(1)
```

```{r}
rnorm(8)
```

```{r}
rnorm(3,0,2)
```

```{r}
rnorm(5,mean=2, sd= 5)
```


## Binomial Distribution
**rbinom(n, size, prob)**  
`rbinom()` function enables us to generate random deviates based on *binomial distribution*.  
Size would be set as *number of trials*.  
Prob would be set as *probability of success on each trial*.  


```{r}
rbinom(10,20,0.1)
```


## seed
Random numbers and not literally 'random' numbers.  
In fact, they are generated based on certain function.  

`set.seed()` makes generated 'random' numbers the same.

```{r}
rnorm(5)
```

```{r}
rnorm(5)
```

```{r}
set.seed(5)
rnorm(5)
```

```{r}
set.seed(5)
rnorm(5)
```


*Note*  
It doesn't mean that after setting seed, you will always get the same output when generating random numbers.  
Instead, after setting seed, we will get the same random numbers generating sequence thereafter.  

```{r}
set.seed(5)
rnorm(5)
rnorm(5)
```

```{r}
set.seed(5)
rnorm(5)
rnorm(5)
```




# Loop


## for
for(variable in vector)
{
 statements
}

```{r}
n = 0
for(i in 1:10)
{
  n = n+ i
}
print(n)
```

**Range could be numeric or character**

```{r}
x <- c("Microeconomics", "Macroeconomics", "Statistics")
for (i in x){
  print(paste("I don't like", i))
}
```

`paste()` is the function to concate two character strings together.  


## While
while(condition)
{
 statements
}

As long as the condition is right, we would continue doing the statements.  


```{r}
n = 0
sum = 0
while(n <10)
{
  sum = sum + n
  n = n + 1
}
sum
```

### Question
1. Calculate the sum from one to twenty through `for` and `while`
2. Calculate the multiplication from one to twenty through `for` and `while`