---
title: "ANOVA"
author: "Jesse"
date: "2019¦~12¤ë3¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

**ANOVA**, analysis of variance,  based on compare *between-group* variances & *within-group* variances.  
And we reject H~0~ if between-variance significantly > within-variance.

We use `aov` function to conduct ANOVA.  
Meanwhile, we have to do two more things to conduct our ANOVA.  

1. We have to change variables into **categorical variable** before conduct ANOVA.
2. We have to furthur use `summary` to see the result.


Here we use dataset **babies**.(https://www.openintro.org/stat/data.php?data=babies)  
In `babies`, researchers investigate a range of topics about pregnancies and infants.  
We wanna see that whether average birthweight varies with mother's age.  

- bwt: birthweight
- gestation: length of gestation
- age: mother's age in years


## Load dataset.
After loading dataset, we try filtering out the missing values.  

```{r}
babies <- read.csv("C:/Users/asus/Desktop/TA/TA session/week12/babies.csv")
babies <- babies[complete.cases(babies),]
```

## Convert age into categorical variables.
We did this by convert *age* into **factor**.  

```{r}
babies$age <- factor(babies$age)
```

And we use `levels` to see how many ages do we have.
```{r}
levels(babies$age)
```


## Plots
As there are too many different ages in the dataset,  
we directly use some plots to see the difference.


```{r}
## Boxplot
ggplot(data=babies) +
  geom_boxplot(mapping = aes(x=age, y=bwt))

##Barplot
ggplot(data = babies) +
  geom_histogram(mapping = aes(x=bwt, fill=age), binwidth = 10)
```


## ANOVA test
Finally, we conduct anova test to see the result.  

```{r}
aov_result <- aov(bwt~age, data = babies)
summary(aov_result)
```


### Question
1. Check whether average length of gestation varies with mother's age.
2. Use dataset **mlb_player_18** (https://www.openintro.org/stat/data.php?data=mlb_players_18).  Check whether average *AVG* varies with *position*.  Filter out data with missing values or where it's *AB* < 10.
