---
title: "t-Test_2"
author: "Jesse"
date: "2019¦~12¤ë2¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```


## Two independent samples
The independent sample t-test is used to compare two means between two groups.  
At the previous course, we had two values for each type.  

ex.  
 Bookstore1 Bookstore2  
Book1 500 600  
Book2 800 900  
Book3 450 655  
Book4 555 666  
Book5 878 997  

We use `t.test(Bookstore$1, Bookstore$2)`.  


This time, we gonna go through dataset of different type.

ex.  
Height Gender  
 158 Female  
 155 Female  
 180 Male  
 177 Male  
 160 Female  
 150 Female  
 168 Male  

Under such circumstances, we have to use `t.test(height~gender, data=height)`.  

Here we use dataset **babies**.(https://www.openintro.org/stat/data.php?data=babies)  
In `babies`, researchers investigate a range of topics about pregnancies and infants.  
We wanna see that `whether it's a first pregnancy`, `whether mother smokes` have impacts on `infant's birthweight`.  

- bwt: birthweight
- gestation: length of gestation
- parity: indicator for a first pregnancy
- smoke: binary indicator for whether the mother smokes.


### Load dataset and filter out the missing values.  
Firstly, we use `read.csv` to load dataset.  


```{r}
babies <- read.csv("C:/Users/asus/Desktop/TA/TA session/week12/babies.csv")
head(babies)
```

As we can see, there are some **NA** in the dataset.  
Therefore, we use `complete.cases` to filter out the NA values.  
`complete.cases` returns a logical vector indicating which cases are complete.   

```{r}
head(complete.cases(babies))
```

With such, we can filter out the **NA** values in datatset.  

```{r}
babies <- babies[complete.cases(babies),]
```

After completing filtering out, here we try conduct some easy analytics.


### Easy Analytics

Here we see the difference between smoke or not.  

```{r}
babies[babies$smoke==1,] %>%
  summarize(n(),
            mean(bwt),
            sd(bwt),
            min(bwt),
            max(bwt))

babies[babies$smoke==0,] %>%
  summarize(n(),
            mean(bwt),
            sd(bwt),
            min(bwt),
            max(bwt))

```

And see the difference between first pregnancy or not.  

```{r}
babies[babies$parity==1,] %>%
  summarize(n(),
            mean(bwt),
            sd(bwt),
            min(bwt),
            max(bwt))

babies[babies$parity==0,] %>%
  summarize(n(),
            mean(bwt),
            sd(bwt),
            min(bwt),
            max(bwt))
```

Meanwhile, we use plots to go through data more clearly.  

**Histogram**  

```{r}
hist(babies[babies$parity==1,]$bwt)

hist(babies[babies$parity==0,]$bwt)
```

```{r}
hist(babies[babies$smoke==1,]$bwt)

hist(babies[babies$smoke==0,]$bwt)
```


**Boxplot**  

```{r}
ggplot(data = babies) + 
  geom_boxplot(mapping = aes(group=parity, x=parity, y=bwt))
```

```{r}
ggplot(data = babies) + 
  geom_boxplot(mapping = aes(group=smoke, x=smoke, y=bwt))
```

### Conduct t-statistics
Finally, let's conduct t statistics for parity and smoke.  


```{r}
t.test(bwt~parity, data = babies)
t.test(bwt~smoke, data = babies)
```


### Question 
Check whether there's difference in `average length of gestation` between `whether it's a first pregnancy` and `whether mother smokes`