---
title: "Matrices"
author: "Jesse"
date: "2019¦~10¤ë22¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```

**Matrices** are used in Econometrics a lot. Therefore, we have to get used to them, knowing how to conduct arithmetics.  

## Creating Matrices
We can use `matrix` to create matrix, or use `as.matrix` to turn variables of other data type into matrix. 
`matrix(data= NA, ncol = 1, nrow = 1, byrow = FALSE)`

```{r}
matrix(1:20,nrow = 4, ncol = 5, byrow = FALSE)
```

```{r}
matrix(1:20, nrow = 4, ncol = 5, byrow = TRUE)
```

We could use `cbind()` or `rbind()` to combine several vectors or elements into one matrix.

```{r}
x <- c(1:4)
y <- c(2:5)

cbind(x,y)
rbind(x,y)
```

`dim` gives you the dimension of the matrix.

```{r}
dim(rbind(x, y))
```

## Column / Row names
We could use `colnames()` and `rownames()` to call or look the names of each column / row  

```{r}
w<- matrix(4:6, nrow = 1, ncol = 3, byrow = FALSE)
rownames(w) <- c("Wow")
colnames(w) <- c("I", "love", "that")
print(w)

```

When we use `cbind()` or `rbind()`, the names of the variables will turned into the names of rows or columns.  

```{r}
John <- seq(108,102,-2)
Mary <- rep(c(3,5), times=1, each=2)
John_Mary <- cbind(John, Mary)
print(John_Mary)
```

## Basic arithmetics function

- `t(x)` : transpose of x
- `%*%` : multiplication
- `det(x)` : determinant
- `solve(x)` : inverse matrix

```{r}
matrix_one <- matrix(2:5, nrow = 2, ncol = 2)
matrix_two <- matrix(6:9, nrow = 2, ncol = 2)
matrix_one
matrix_two
```

```{r}
t(matrix_one)
```

```{r}
three <- matrix_one %*% matrix_two
three
```

```{r}
det(matrix_one)
```

```{r}
solve(matrix_one)
```

## Data Extraction

```{r}
m <- matrix(1:20, nrow =4, ncol = 5)
colnames(m) <- c("Math", "Chinese", "Spanish", "Science", "English")
rownames(m) <- c("One", "Two", "Three", "Four")
print(m)
```

Then you can extract data by index.  

```{r}
m[4,5]
```

```{r}
m[2,]
```

```{r}
m[,c(1:3)]
```

Extract fata by name

```{r}
m["One", "Math"]
```

```{r}
m[,c("English", "Spanish")]
```


### Question
John, Mary and Jean all had three tests for Econometrics. Here's their grades:  
- John: 70,59,61  
- Mary: 66,88,98  
- Jean: 84,88, 79  
Make a matrix of it.
