---
title: "Ifelse¡Bfunction"
author: "Jesse Chang"
date: "2019¦~10¤ë1¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
```

# Conditional Operators
1. ifelse  
2. if¡Belse if ¡Belse  

## ifelse
IFelse returns a value for true or false.  
**ifelse(test, true, false)**

Let us give some examples.  
```{r}
x <- 6
y <- ifelse(x >12, 2,10)
y
```

```{r}
x <- 50
y <- ifelse(x>10, 5, 8)
y
```

It also works with `&` and `|` statements

```{r}
x <- 10
y <- ifelse(x>5 & x <12, 5 ,10)
y
```

```{r}
x <- 12
y <- ifelse(x>0 | x < -2, 222, 666)
y
```

## if + else if + else


if(condition 1)  
{  
  Statements 1  
} else if(condition 2)  
{  
  Statements 2  
}...
 else if(condition k)  
{  
  Statements k  
} else  
{  
  Statemtns k+1  
}  

```{r}
x = 20
if(x <1)
{
  y = 5
  z = 10
}else if (x <10 & x >=1)
{
  y = 10
  z = 20
}else
{
  y = 20
  z = 40
}
print(c(y,z))
```

### Question
1. Create one conditional statements with two `else if`  
2. Turn the following statements into if else condition.  
1) Johnny has 3 apples. If Johnny has more than 5 apples, Doris will have 5; If not, Doris will gave 6. Print out how many apples Doris has. Hint:Do it with `ifelse`  
2) Tim has 5 apples. If he has more than 6 apples, he would say "I have many apples"; if he has more than 3 but less than 6 apples, he would say "I have some apples"; if he has less than 3, he would say "I have few apples". Hint: Do it with `if else if else `   




# Function
A function is a set of statements organized together to perform a specific task.  
R has a large number of in-built functions such as `geom_point()`¡B`ggplot()` and we can create our own functions.  

**Function Definition**  
function_name <- function(arg1, arg_2, ...)
{
  Function body
}

- Function Name: the name of the function
- Arguments : When a function is invoked, you pass a value to the function by the arguments. There are optional; you can assign default values to arguments.
- Function Body : A collection of statements defining what the function does.

## Built-in Function
`seq()`, `mean()`, `sum()` etc.  
They are directly called by written programs.

```{r}
print(seq(25:50))
print(sum(25:50))
```

## User-defined Function


```{r}
new_function <- function(a)
{
  if (x >2)
    print(3)
  else
    print(5)
}
new_function(5)
```

**We can create a function without any argument.**

```{r}
new_func_no_arg <- function()
{
  print("No arguments")
}
new_func_no_arg()
```

**Meanwhile, we can call a function with default arguments.  **

If there's new value toward the arguments, the default value could be replaced.

```{r}
new_func_with_default <- function(a = 3, b =6)
{
  result <- a*b
  print(result)
}
new_func_with_default()
new_func_with_default(9,7)
new_func_with_default(10)
```


## Calling a function with arguments
You can call a function with arguments and call arguments either **by position** or **by name**.  
The arguments to a function can be supplied in the same sequence or can be supplied in a different sequence but assigned with the names of the arguments.

```{r}
new_func_arg <- function(a,b,c)
{
  result <- a*b / c
  print(result)
}
new_func_arg(5,3,15)
new_func_arg(b=12, a = 20, c = 3)
```





### Question
1. How to assign values only to argument b in `new_func_with_default`  
2. Make a function to see whether the passed number is the multiple of 3