---
title: "Chi-square Test"
author: "Jesse"
date: "2019¦~11¤ë18¤é"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

# Chi-Square Test.

Today we learn how to do chi-square test toward data.

You may download *Smoking* data from https://www.openintro.org/stat/data.php?data=smoking.  
It surveys the smoking habit in UK.  

Some important variables explained in the following:  

- gender : Gender with levels Female and Male.
- nationality : Nationality with levels British, English, Irish, Scottish, Welsh, Other, Refused and Unknown.
- marital_status : Marital status with levels Divorced, Married, Separated, Single and Widowed.

- smoke : Smoking status with levels No and Yes

Today, we gonna test if the above three variables have association with the smoking habit.

## Read data.
As usual, we use `read.csv` to read csv files.

```{r}
smoking <- read.csv("C:/Users/asus/Desktop/TA/TA session/week10/smoking.csv")
```

## Basic data analysis.
We wanna to know more about the relation between smoke and *gender, nationality, marital_status* respectively.
Here, we produce *a contingency table of percentage * and *do some plots*.

Firstly, we conduct plots to see the distribution of smoke or not filter by the *gender, nationality, marital_status*.  
Here, we found that *barplot* would help a lot.

```{r}
ggplot(data = smoking) + 
  geom_bar(mapping = aes(x=smoke, fill=marital_status), position = "dodge")

ggplot(data = smoking) + 
  geom_bar(mapping = aes(x=smoke, fill=nationality), position = "dodge")

ggplot(data = smoking) + 
  geom_bar(mapping = aes(x=smoke, fill=gender), position = "dodge")
```

Secondly. we try conducting contingency table of percentage to furthur see the distribution by percentage.

```{r}

gender.smoke <- table(smoking$smoke, smoking$gender)
gender.smoke.pro <- prop.table(gender.smoke, margin = 2)
print(gender.smoke.pro)

marital.smoke <- table(smoking$smoke, smoking$marital_status)
marital.smoke.pro <- prop.table(marital.smoke, margin = 2)
print(marital.smoke.pro)

nationality.smoke <- table(smoking$smoke, smoking$nationality)
nationality.smoke.pro <- prop.table(nationality.smoke, margin = 2)
print(nationality.smoke.pro)

```

## Conduct chi-square test.
Finally, we conduct chi-square test to see if the three variables have association with smoke.

```{r}
chisq.test(gender.smoke)

chisq.test(marital.smoke)

chisq.test(nationality.smoke)
```

if we set a = 0.05
We can see **marital_status. nationality** both have association with smoking habit.



### Question
You may donwload *absenteeism* dataset from https://www.openintro.org/stat/data.php?data=absenteeism .  
Reserachers collected data from 146 randomly sampled students in rural New South Wales, Australia, in a particular school year.  

Some important variables explained in the following:  

- sex : Gender.
- lrn : Learner status, with average learner (`AL`) and slow learner (`SL`).

We wanna test if there's strong association between gender and learning status.
a = 0.05.

1. Make a two-way by-percentage contingency table of the sex and lrn.
2. Do some plots to know more about them.
3. Do chi-suare test.